Fluent statistical computing interfaces for biological data analysis

### 2020-02-24 Rmd/01-intro.Rmd
update toc; rebuild

Exploratory data analysis (EDA) is a vital element of the modern 
statistical workflow - it is an analyst’s first pass at 
understanding their data; revealing all it’s messes and (possibly) 
uncovering hidden insights [@Tukey1977-pn; @Grolemund2017-uc]. 
It is an iterative process invovling both computation and visualization 
that can generate new hypotheses that can be tested and formalised using 
stastical modelling. Moreover, as datasets grow in complexity and become
increasingly heterogenous and multidimensional, 
the use of EDA becomes vital to ensure the integrity and quality of analysis 
outputs.  This is certainly true in high-throughput biological 
data analysis, where there are constraints on computation time and 
memory, leading to the situation that as data becomes larger,
EDA becomes increasingly difficult.

>>>>

Exploratory data analysis (EDA) is a vital element of the modern 
statistical workflow - it is an analyst’s first pass at 
understanding their data; revealing all it’s messes and (possibly) 
uncovering hidden insights [@Tukey1977-pn; @Grolemund2017-uc]. 
It is an iterative process involving both computation and visualization 
that can generate new hypotheses that can be tested and formalised using 
statistical modelling. Moreover, as datasets grow in complexity and become
increasingly heterogeneous and multidimensional, 
the use of EDA becomes vital to ensure the integrity and quality of analysis 
outputs.  This is certainly true in high-throughput biological 
data analysis, where there are constraints on computation time and 
memory, leading to the situation that as data becomes larger,
EDA becomes increasingly difficult.
